Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-13 journal/content.tex
Bias towards successful transformations

% Defence against criticism for weak evidence in primary studies
\subsection{Possible weakness of evidence due to primary study quality}

@@

>>>>

% Defence against criticism for weak evidence in primary studies
\subsection{Possible weakness of evidence and bias due to primary study quality}

@@

A tendency to publish only positive results is another particular problem for
this literature review. In the collection of primary studies it can be observed
that authors typically considered the transformation being successful.
It can be argued that this apparent tendency to publish only cases that have
experienced success will bias the results.
However, even if the transformations were considered successful in general, most
studies brought up different challenges that had been experienced during the
transformation.
